Convex Surrogates via Polyhedral Losses

### 2019-04-26 neurips-19/cvx-fin.tex
Small typo and formatting things.

\documentclass[12pt]{article}
\PassOptionsToPackage{numbers, compress}{natbib}
\usepackage[preprint]{neurips_2019}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks  %[implicit=false, bookmarks=false]
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

@@

\begin{abstract}
  We formalize and investigate the natural approach of designing convex surrogate loss functions via embeddings, for problems such as classification or ranking which involve a finite number of possible predictions.
  Specifically, we consider surrogate losses given by embedding each prediction (label, ranking, etc) as a point in $\reals^d$, and convexifying the loss.
  We prove that this approach is equivalent to working with polyhedral (piecewise linear convex) losses, in several strong senses.
  We then investigate the dimensionality of the surrogate hypothesis space required for such an embedding, giving a complete characterization of the 1-dimensional case.
  We illustrate our results with modest lower bounds for abstain loss, and conclude with future directions.
\end{abstract}

@@

Convex surrogates have been formalized and investigated in a variety of past work such as \cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification}, particularly in the context of $0-1$ loss, distributions on just two outcomes, and support vector machines.

@@

  \cite{agarwal2015consistent} and ~\cite{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g. \jessiet{take out of math mode} $0-1$ loss via their notion of feasible subspace dimension.

@@

We write loss functions as $L:\R\to\reals^\Y_+$ which map a report (prediction) $r\in\R$ to the vector of loss values $L(r) = (L(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
Often $\R$ will be taken to be a finite set for the given discrete loss (in which case we will write $\ell$ not $L$), and $\reals^d$ for the surrogate.
The expected loss of report $r$ when $y \jessie{Y} \sim p$ is written $\inprod{p}{L(r)}$.
For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$ given by $\ell(r)_y = \Ind[r \neq y]$.
Two important examples of surrogates for 0-1 loss, with $\R=\reals$, are hinge loss $L(u)_y = \max(0,1-yu)$ and logistic loss $L(u)_y = \log(1+\exp(-yu))$.

>>>>

\documentclass[12pt]{article}
\PassOptionsToPackage{numbers, compress}{natbib}
\usepackage[submission]{neurips_2019}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks  %[implicit=false, bookmarks=false]
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

@@

\begin{abstract}
  We formalize and investigate the natural approach of designing convex surrogate loss functions via embeddings, for problems such as classification or ranking which involve a finite number of possible predictions.
  Specifically, we consider surrogate losses given by embedding each prediction (label, ranking, etc) as a point in $\reals^d$, and ``convexifying'' the loss.
  We prove that this approach is equivalent to working with polyhedral (piecewise linear convex) losses, in several strong senses.
%  We then investigate the dimensionality of the surrogate hypothesis space required for such an embedding, giving a complete characterization of the 1-dimensional case.  \jessiet{Remove this from the abstract.}
  We illustrate our results with modest lower bounds for abstain loss, and conclude with future directions.
\end{abstract}

@@

Convex surrogates have been formalized and investigated in a variety of past work such as \cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification}, particularly in the context of 0-1 loss, distributions on just two outcomes, and support vector machines.

@@

  \cite{agarwal2015consistent} and ~\cite{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g. 0-1 loss via their notion of feasible subspace dimension.

@@

We write loss functions as $L:\R\to\reals^\Y_+$ which map a report (prediction) $r\in\R$ to the vector of loss values $L(r) = (L(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
Often $\R$ will be taken to be a finite set for the given discrete loss (in which case we will write $\ell$ not $L$), and $\reals^d$ for the surrogate.
The expected loss of report $r$ when $Y \sim p$ is written $\inprod{p}{L(r)}$.
For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$ given by $\ell(r)_y = \Ind[r \neq y]$.
Two important examples of surrogates for 0-1 loss, with $\R=\reals$, are hinge loss $L(u)_y = \max(0,1-yu)$ and logistic loss $L(u)_y = \log(1+\exp(-yu))$.
